---
title: "PM566 Final Project"
author: "Amei Hao"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

<br>

This is my PM566 Final Project website. I will showcase a few interactive visuals here.

(Your output should look something like this)

<br>
# Lab12
```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)

# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = TRUE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```

```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

<br>

## First step

First I will source any necessary code, e.g. `process_covid_data.R`:

```{r load-data}
source("process_COVID_data.R")
```

<br>

## Second step

Then I will add some code to create the **plotly** figures

Note: You need to name each code chunk, like this one: `plot1`

```{r plot1, class.source="code-r-small"}

p1_scatter <- cv_states_today %>% 
  plot_ly(x = ~pop_density, y = ~deathsper100k,
          type = 'scatter', mode = 'markers', color = ~state,
          size = ~population, sizes = c(5, 70), marker = list(sizemode='diameter', opacity=0.5),
          hoverinfo = 'text',
          text = ~paste( paste(state, ":", sep=""), paste(" Cases per 100k: ", per100k, sep="") , paste(" Deaths per 100k: ",
                        deathsper100k, sep=""), sep = "<br>")) %>%
  layout(title = "Population-normalized COVID-19 deaths vs. population density",
                  yaxis = list(title = "Deaths per 100k"), xaxis = list(title = "Population Density"),
         hovermode = "compare")

# filter out "District of Columbia"
cv_states_today_scatter <- cv_states_today %>% filter(state!="District of Columbia")

p2_scatter <- cv_states_today_scatter %>% 
  plot_ly(x = ~pop_density, y = ~deathsper100k,
          type = 'scatter', mode = 'markers', color = ~state,
          size = ~population, sizes = c(5, 70), marker = list(sizemode='diameter', opacity=0.5),
          hoverinfo = 'text',
          text = ~paste( paste(state, ":", sep=""), paste(" Cases per 100k: ", per100k, sep="") , paste(" Deaths per 100k: ",
                        deathsper100k, sep=""), sep = "<br>")) %>%
  layout(title = "Population-normalized COVID-19 deaths vs. population density",
                  yaxis = list(title = "Deaths per 100k"), xaxis = list(title = "Population Density"),
         hovermode = "compare")
```

<br>

## Third step {.tabset}

Create tabs to display each figure

### Scatterplot: with DC

```{r p1}
p1_scatter
```

### Scatterplot: without DC

```{r p2}
p2_scatter
```

## {-}

<br>

Done!

<br>
<br>


# Assignment 05 - Interactive Visualization I and II

Using your midterm/final project data, create 3 different interactive visualizations using the tools learned in week 11 class/lab.

Include the visualizations created in 1. on your github.io website.
```{r}
# Prep the data 
library(data.table)
library(dplyr)
library(dtplyr)
library(ggplot2)
library(plotly)
library(lubridate)
library(leaflet)
library(knitr)
library(kableExtra)
library(lubridate)


# Download the data and read into data table
crime<- data.table::fread("/Users/amei/Documents/PM566-Midterm-Project/Crime_Data_from_2020_to_Present.csv")
rob <- crime[which(crime$'Crm Cd Desc' == 'ROBBERY')]
```

```{r}
# deal with the missing data in vict sex
sex_missing <- sum(rob$`Vict Sex`=='') + sum(rob$`Vict Sex`=='X') + sum(rob$`Vict Sex`=='H')
sex_missing/length(rob$`Vict Sex`)
# deal with the missing data in vict age
age_missing<- sum(rob$`Vict Age`== 0) + sum(rob$`Vict Age`=='')
age_missing/length(rob$`Vict Age`)
# deal with the missing data in time
time_missing<-sum(rob$`TIME OCC`=='')
# Remove the missing values,unclear and implausible values we found in the previous step
time_missing/length(rob$`TIME OCC`)
rob_new<- rob[which(rob$`Vict Sex` != '' & rob$`Vict Sex` != 'X')]
rob_new<- rob_new[which(rob_new$`Vict Age` != 0 & rob_new$`Vict Age` != '')]
```
### Hist of Age by Time

```{r}
rob_new$time<- cut(rob_new$`TIME OCC`, 
               breaks=c(0, 600, 1200, 1800, 2400),
               labels=c("before dawn","moring","afternoon","night"), 
               right = FALSE)

rob_new %>%
  filter(!(rob_new$time %in% NA)) %>% 
  ggplot()+ geom_histogram(mapping=aes(x=rob_new$`Vict Age`,fill=rob_new$time))+
  scale_fill_brewer(palette = "PuBu")+labs(title="Age by Time category", x="Victom Age", y="count")
```
### Barchart of Sex

```{r}
ggplot(rob_new,aes(x =`Vict Sex`)) + geom_bar(stat = 'count', fill = 'lightpink', colour = 'pink') + labs(title = "Freqs by sex")
```
### Barchart of Age
```{r}
ggplot(rob_new,aes(x =`Vict Age`)) + geom_bar(stat = 'count', fill = 'lightblue', colour = 'blue') + labs(title = "Freqs by Age")
```


### Multiple line chart of crime counts by locations in November

```{r plot2, class.source="code-r-small"}
rob_new$`DATE OCC` <- as.Date(substr(rob_new$`DATE OCC`,1,10),"%m/%d/%Y")
rob_new$month_occurance <- month(rob_new$`DATE OCC`)
rl <- rob_new[which(rob_new$month_occurance!=11)]

p <- ggplot(rl,aes(x =month_occurance, group=`AREA NAME`, color = `AREA NAME`)) + geom_line(stat = 'count') +geom_point(stat = 'count')+scale_x_continuous(breaks=seq(0, 11, 1)) 

ggplotly(p)
```
### Scatter plot

```{r,echo = FALSE,warning=FALSE}
library(plotly)
p1 <- ggplot(rob_new)+
  geom_point(mapping = aes(x = `DATE OCC`, y =`Vict Age` , color = `AREA NAME`))+ theme_classic()
ggplotly(p1)
```

### Summary Table

```{r plot3, class.source="code-r-small"}
library(DT)
rs <- rob_new %>% select(`DATE OCC`, `AREA NAME`, `Vict Age`,`Vict Sex`,`Weapon Desc`)
datatable(rs)
```
